Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
num changes rep

The models we consider have two sources of error due to numeric representation. 
The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and $x_k$. 
The second is the quantization error introduced by the digital controller, 
which performs operations in the domain of fixed-point numbers. 
In this section we formally outline the errors introduced by the fixed-point representation of numbers. 
% 
Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part. The smallest number that can be represented in this domain is $c_m=2^{-F}$. Any mathematical operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$ will introduce errors, that can be upper bounded~\cite{DBLP:conf/arith/BrainTRW15}. Further details are in Appendix~\ref{appendix:numerical_errors}.

@@

Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part. The smallest number that can be represented in this domain is $c_m=2^{-F}$.
The following approximation errors will arise in mathematical operations and representation:
\begin{enumerate}
\item {\bf Truncation:}
Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.

>>>>

The models we consider have two sources of error due to numeric representation. 
The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and $x_k$. 
The second is the quantization error introduced by the digital controller, 
which performs operations in the domain of fixed-point numbers. 
In this section we outline the notation for the fixed-point representation of numbers, and briefly describe the errors introduced. A formal outline is in Appendix~\ref{appendix:numerical_errors}.

Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part. The smallest number that can be represented in this domain is $c_m=2^{-F}$. Any mathematical operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$ will introduce errors, that can be upper bounded~\cite{DBLP:conf/arith/BrainTRW15}.

@@

We have  used $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part. The smallest number that can be represented in this domain is $c_m=2^{-F}$.
The following approximation errors will arise in mathematical operations and representation:
\begin{enumerate}
\item {\bf Truncation:}
Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.
